Amicus Word Count

### 2021-11-05 data-cleaning/01-shorten-amicus-text.Rmd
rmv intros from amicus text

# data manip
library(tidyverse)
library(tidytext)
```

@@

* "footnotes" ??

@@

```{r}
amicus <- amicus %>%
  mutate(txt_full = tolower(txt_full),
         txt_full = str_squish(txt_full)) %>% 
  mutate(appendix = str_count(txt_full, "appendix"),
         footnotes = str_count(txt_full, "footnote"))

amicus %>% select(case, brief, appendix, footnotes) %>% 
  group_by(appendix > 0, footnotes >0) %>% 
  summarize(n())
```

```{r}
amicus %>% filter()
```

>>>>

# data manip
library(tidyverse)
library(tidytext)

# data
# data/processed amicus files/shortened-amicus-brief-text.csv
amicus <- box_read("880862059511")
# data/processed amicus files/amicus summary.xlsx
alternate_rmv <- box_read("864995408351", sheet = "data") %>% 
  select(case, brief, id, alternative) %>% 
  filter(!is.na(alternative))
```

@@

# Remove after "Summary of Argument"

For most documents, there exists the header "summary of argument." If it did not exist, it was manually entered into the document. This represents the point at which the brief starts discussing their argument. We don't need text prior to this, as it's mainly intro information about the case and/or the authors. If "summary of argument" text doesn't exist (only in the case of a few pdfs), use the `alternative_rmv` df to find where to start reading the text.

alternate removal strings

```{r}
alternate_rmv %>% select(id,alternative)
```
Shorten

```{r}
# remove text after "summary of argument" if it exists
amicus <- amicus %>% 
  mutate(txt_full = str_to_lower(txt_full),
         txt_full = str_squish(txt_full),
         txt_short = case_when(
           grepl("summary of argument", txt_full) ~ 
             gsub(pattern = ".*summary of argument", replacement = "", x = txt_full),
           grepl("summary of the argument", txt_full) ~
             gsub(pattern = ".*summary of the argument", replacement = "", x = txt_full),
           id == 861820908073 ~ gsub(pattern = ".*introduction and summary", replacement = "", x = txt_full),
           id == 861820896073 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           id == 861822667487 ~ gsub(pattern = ".*introduction", replacement = "", x = txt_full),
           T ~ ""),
         txt_short = str_squish(txt_short))
```

Check none are missed

```{r}
amicus %>% filter(txt_short == "") %>% select(-txt_full)
```

Check a few by running this line a few times.

```{r}
#amicus %>% sample_n(1) %>% pull(txt_short)
```

# Remove text after "Appendix" or "Footnotes"

@@

```{r}
amicus <- amicus %>%
  mutate(appendix = str_count(txt_full, "appendix"),
         footnotes = str_count(txt_full, "footnote"))

amicus %>% select(case, brief, id, appendix, footnotes) %>% 
  filter(appendix==0 & footnotes==0)
```

# Save

Original text saved, just added new txt_short col

```{r}
amicus %>% colnames
```

```{r}
box_write(amicus,
          file_name = "shortened-amicus-brief-text.csv",
          dir_id = '145990409196')
```
